# Methods

To examine the effects of parameter input sensitivity, we developed a trip-based travel model with three steps: 

  1. trip generation, 
  2. trip distribution, and
  3. mode choice.

Trip generation, the first step, was conducted using socioeconomic (SE) data from a 25-zone dummy model of the [ActivitySim GitHub repository](https://github.com/ActivitySim/activitysim). Trip production was estimated using the [2017 National Household Travel Survey data](https://github.com/byu-transpolab/nhts2017) (NHTS2017). The trip productions were summarized by household sizes, vehicles, and workers, and the weighted mean of each trip purpose was taken. The three trip purposes used are Home Based Work (HBW), Home Based Other (HBO), and Non-Home Based (NHB). NHTS2017 data and the SE data were merged based upon their household size, vehicles, and workers with maximum thresholds set as 4 persons, 3 vehicles, and 2 workers per household. Trip attraction was skipped for this analysis.

The second step, trip distribution, used distance and travel time skims from an example in the ActivitySim GitHub repository. The skims were simplified to use auto, nonmotorized, and transit modes. Travel time for auto used the single occupancy vehicle AM time, nonmotorized travel time used the walking distance skim multiplied by a factor of average walking speed, and transit time used the walk to local bus time. 

Mode choice, the third step, calculates utilities for the three modes. These utilities were exponentiated, added together, and the natural log was taken to get a logsum value for every origin and destination pair. The utility equations for the mode choice model are as follows:

\begin{equation}
\mathrm{drive\_utility} = (\mathrm{coeff\_ivtt}*\mathrm{auto})+(\mathrm{coeff\_cost}*\mathrm{auto\_cost}*\mathrm{DIST})
(\#eq:driveutil)
\end{equation}
\begin{equation}
\mathrm{nonmo\_utility} = (\mathrm{k\_nmot}+ 20 * (\mathrm{coeff\_walk1}*\mathrm{nonmotor}))
(\#eq:nonmoutil)
\end{equation}
\begin{equation}
\mathrm{trans\_utility} = \mathrm{k\_trn} + (\mathrm{coeff\_ivtt}*\mathrm{transit})
(\#eq:transutil)
\end{equation}

The mode choice parameters (constants and coefficients) were obtained from the [USTM Resiliency Model](https://github.com/byu-transpolab/ustm_resiliency). These values are shown in Table \@ref(tab:MCcoeff) and Table \@ref(tab:MCconst). 

```{r MCcoeff, echo = FALSE, results = 'axis'}
tar_load(mc_coeff)
mc_coeff2 <- mc_coeff %>%
  filter(Name %in% c("CIVTT", "CCOST", "CWALK1", "AUTOCOST"))
kable(mc_coeff2[,2:5], caption = "Mode Choice Coefficients", booktabs = TRUE)
```

```{r MCconst, echo = FALSE, results = 'axis'}
tar_load(mc_const)
mc_const2 <- mc_const %>%
  filter(Name %in% c("K_TRN", "K_NMOT"))
kable(mc_const2[,2:5], caption = "Mode Choice Constants", booktabs = TRUE)
```

With this simple three-step model, MC and LHS methods were used to determine the possible combinations of parameter variance. To identify a standard deviation for each parameter, a coefficient of variation was used. A set coefficient of variation of 0.30 was used for all six input parameters [@zhao2002propagation]. The standard deviation was equal to 0.30 multiplied by the mean, where the mean values in this situation are the base scenario parameters (as identified in Table \@ref(tab:MCcoeff) and Table \@ref(tab:MCconst)).

The MC random sampling uses the R function of `rnorm`. LHS uses the `lhs` package in R. Since this package only chooses variables on a zero to one scale, the values given use a function to put the random sampling on the right scale needed for the given parameter. The full code for both methods can be found in a public 
[GitHub repository](https://github.com/natmaegray/ustm_resiliency_sensitivity). 100 and 600 draws of random samples for both methods are generated. With these generated parameters, the mode choice model step was run for every set of input parameters for each purpose. The mean logsum value for each run was determined to compare each continuous draw. 