# Methods

To examine the effects of parameter input sensitivity, a 25 zone dummy model was created using data from <https://github.com/ActivitySim/activitysim>, and coefficient values from the USTM Resiliency Model.

The inputs for sampling that will be used are mode choice coefficients, mode choice constants, and destination choice parameters. These inputs are shown in Table \@ref(tab:MCcoeff), and Table \@ref(tab:MCconst).

```{r MCcoeff, echo = FALSE, results = 'axis'}
tar_load(mc_coeff)
mc_coeff2 <- mc_coeff %>%
  filter(Name %in% c("CIVTT", "CCOST", "CWALK1", "AUTOCOST"))
kable(mc_coeff2[,2:5], caption = "Mode Choice Coefficients")
```

```{r MCconst, echo = FALSE, results = 'axis'}
tar_load(mc_const)
mc_const2 <- mc_const %>%
  filter(Name %in% c("K_TRN", "K_NMOT"))
kable(mc_const2[,2:5], caption = "Mode Choice Constants")
```

```{r DCparam, echo = FALSE, results = 'axis'}
#tar_load(dc_param)
#kable(dc_param[,2:5], caption = "Destination Choice Parameters")
```

The shapefile for the dummy model is shown in Figure \@ref(fig:TAZmap). 

```{r TAZmap, echo = FALSE, fig.align="center", results='asis', fig.cap = "TAZ Map with ID"}
tar_load(map_plot)
map_plot
```

A mode choice model was created with utility equations for Home Based Work Trips(HBW), Home Based Other Trips(HBO), and Non Home Based Trips(NHB). 

A coefficient of variation is used for each input parameter to determine a range for the values that can be used within the model, to estimate the sensitivity of these parameters.

The initial model was run, the change was calculated on a random selection basis, and then using latin hyoercube sampling, to see if latin hypercube sampling can estimate uncertainty in fewer runs.
